The Effects of the 2023 Rule Changes in Major League Baseball

### 2023-11-09 manuscript/paper.tex
added barplot figure and description to manuscript data section

>>>>

One of the main reasons commissioner Rob Manfred enacted the pitch clock ``rule''
was to speed up the games and improve the pace of play to make them more engaging
for the fans, and preliminary analysis shows this worked. Notice in Figure~\ref{fig:Fig1}
the average length of games for the 2023 season was the shortest in the past 25 years.
There is some season-to-season variation but the highlighted yellow bar on the right
(representing the 2023 season) seems significantly lower than the rest. We will
test if the difference in average game length between 2023 and 2022 is statistically
significant in Section~\ref{sec:meth}.

\begin{figure}[tbp]
  \centering
  \includegraphics{barplot_glength}
  \caption{Average Game Length in hours for all MLB games from 1998 to 2023.}
  \label{fig:Fig1}
\end{figure}
